Cosmology with weak lensing photometric surveys: constraints with redshift tomography of non--Gaussian statistics

### 2016-04-26 photoz_paper/paper.tex
added acknowledgements

\begin{figure*}
\includegraphics[scale=0.3]{Figures/constraints_Om-w_lensing.eps}
\includegraphics[scale=0.3]{Figures/constraints_Om-w_lensing_cmb.eps}
\caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}). The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been computed from $16000$ summary statistics realizations, and have been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-sized survey. The thick line ellipses in the right panel refer to $(\Omega_m,w)$ obtained from the weak lensing statistics considered in this work, but subject to Planck priors as described in equation (\ref{meth:parcovestimator_cmb}).}
\label{fig:constraintsOm-w}
\end{figure*}

@@

We thank Colin Hill for useful discussions. The simulations in this work
were performed at the NSF XSEDE facility, supported by grant number
ACI-1053575, and at the New York Center for Computational Sciences, a
cooperative effort between Brookhaven National Laboratory and Stony
Brook University, supported in part by the State of New York. This
work was supported in part by the U.S. Department of Energy under
Contract Nos. DE-AC02-98CH10886 and DE-SC0012704, and by the NSF Grant
No. AST-1210877 (to Z.H.) and by the Research Opportunities and
Approaches to Data Science (ROADS) program at the Institute for Data
Sciences and Engineering at Columbia University (to Z.H.).

>>>>

\begin{figure*}
\includegraphics[scale=0.3]{Figures/constraints_Om-w_lensing.eps}
\includegraphics[scale=0.3]{Figures/constraints_Om-w_lensing_cmb.eps}
\caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}). The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been computed from $16000$ summary statistics realizations, and have been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-sized survey. The thick line ellipses in the right panel refer to $(\Omega_m,w)$ obtained from the weak lensing statistics considered in this work, but subject to Planck priors as described in equation (\ref{meth:parcovestimator_cmb}). The thin solid lines in the left and right panels are the same.}
\label{fig:constraintsOm-w}
\end{figure*}

@@

We thank Colin Hill and Licia Verde for useful discussions. We also thank Martin Kilbinger, Lloyd Knox and Hu Zhan for comments on an earlier version of this manuscript.
The simulations in this work were performed at the NSF XSEDE facility, supported by grant number
ACI-1053575, and at the New York Center for Computational Sciences, a
cooperative effort between Brookhaven National Laboratory and Stony
Brook University, supported in part by the State of New York. This
work was supported in part by the U.S. Department of Energy under
Contract Nos. DE-AC02-98CH10886 and DE-SC0012704, and by the NSF Grant
No. AST-1210877 (to Z.H.) and by the Research Opportunities and
Approaches to Data Science (ROADS) program at the Institute for Data
Sciences and Engineering at Columbia University (to Z.H.).
